A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-19 paper/prab.tex
more changes according to our discussion

%\noindent\begin{minipage}{0.48\textwidth}
%\noindent
\begin{code}[Assembling the optimizer \\ from components]
typedef OpalInputFileParser Input_t;
typedef PisaVariator        Opt_t;
typedef OpalSimulation      Sim_t;

>>>>

%\noindent\begin{minipage}{0.48\textwidth}
%\noindent
\begin{code}[Assembling the optimizer \\ from components]
typedef  \textsc{OPAL-t} InputFileParser Input_t;
typedef PisaVariator        Opt_t;
typedef OpalSimulation      Sim_t;

### 2018-07-19 paper/theor-experiment.tex
more changes according to our discussion

All numerical experiments in this sections were executed on the
  \textsc{Felsim} cluster at PSI\@.
The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
  cores.
The nodes are connected via Infiniband network with a total bandwidth of 16
  GB/s.

@@

For validation purposes we compared the results of the envelope-tracker using
  the analytical space charge model with the \textsc{OPAL-T} 3D macro particle
  tracker.
The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
  MeV injector.
The results for both rms beam size and emittance are shown in
  Figure~\ref{fig:et-vs-tt}.
A good agreement between the two codes can be observed.
The difference of the larger emittance along the solenoids in case of 3D
  tracker that is not seen by the envelope-tracker is due to the different
  definition of the particle momenta (canonical vs.~mechanical).
Both trackers agree within acceptable limits \cite{chao:99}.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are weighted 
equally and calculated at 
$s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
beam line elements. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

>>>>

%All numerical experiments in this sections were executed on the
%  \textsc{Felsim} cluster at PSI\@.
%The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
%  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
%  cores.
%The nodes are connected via Infiniband network with a total bandwidth of 16
%  GB/s.

@@

For validation purposes we compared the results of the envelope-tracker using
  the analytical space charge model with the \textsc{OPAL-t} 3D macro particle
  tracker.
The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
  MeV injector.
The results for both rms beam size and emittance are shown in
  Figure~\ref{fig:et-vs-tt}.
A good agreement between the two codes can be observed.
The difference of the larger emittance along the solenoids in case of 3D
  tracker that is not seen by the envelope-tracker is due to the different
  definition of the particle momenta (canonical vs.~mechanical).
Both trackers agree within acceptable limits \cite{chao:99}.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are weighted 
equally and calculated at 
$s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
beam line elements. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24 \ldots 25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}
